A Partitioning Algorithm for Maximum Common (Connected) Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-10 paper/paper.tex
Wrote a bit more about extensions and experiments

\citet{UpcomingAAAIPaper}

\citet{DBLP:conf/cp/McCreeshNPS16}

\citet{DBLP:conf/cp/NdiayeS11}

@@

For the variant in which the common subgraph must be connected, we consider
only undirected graphs. We modify the algorithm by permitting branching only on
a vertex $v$ that has at least one non-zero element in its bitstring label.
(Cite the first paper that did this.) ? Should we say that smarter propagation
might be possible?

@@

Dual Xeon E5-2640 v2 CPUs, 64GBytes RAM. Parallel experiments 32 threads, using
all 16 physical cores with hyper-threading enabled.

>>>>

@@

\paragraph{Maximum Common \emph{Connected} Subgraph} For the variant in which
the common subgraph must be connected, we consider only undirected graphs. We
modify the algorithm by permitting branching only on a vertex $v$ that has at
least one non-zero element in its bitstring label.  (Cite the first paper that
did this.) ? Should we say that smarter propagation might be possible?

\paragraph{Almost Subgraph Isomorphism} \citet{UpcomingAAAIPaper} present a
``top-down'' algorithm for Maximum Common Subgraph in which a solution of size
$n_G$ is initially sought; if such a solution does not exist then this
solutions of size $n_G-1, n_G-2, \dots$ are sought in sequence.  This strategy,
when used with techniques based on a state-of-the-art subgraph isomorphism
solver, outperformed CP and clique encodings on a large benchmark set of graph
pairs.  We can modify the \McSplit\ algorithm to use the top-down strategy by
calling the main \FuncSty{McSplit} method once per goal size ($n_G, n_G-1,
n_G-2, \dots$).  We backtrack (\lineref{PruneSearch} of Algorithm~\ref{jtAlg})
when the bound is strictly less than the goal size, and terminate when a
solution of the goal size is found.

@@

Our experiments were performed on a cluster of machines with Dual Xeon E5-2640
v2 CPUs and 64GBytes RAM. Parallel experiments used 32 threads per machine,
using all 16 physical cores with hyper-threading enabled.

For all experiments except the top-down ones, we used a database of
randomly-generated Maximum Common Subgraph instances, which contains graphs of
order ranging from 10 to 100 vertices
\cite{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}.  For
unlabelled instances, we selected 10 per cent of the 41,100 instances with up
to 40 vertices; labels were discarded. For labelled instances, we selected 10
per cent of the full database of 81,400 instances, and used a labelling scheme
in which then number of distict vertex labels and the number of distinct edge
labels is approximately equal to 33 per cent of the number of vertices in each
graph (? re-word, give original reference for labelling scheme).

(? Ciaran, while I remember to ask: what should a program do if it is running
undirected, labelled and the same edge appears twice in the input in opposite
directions? My program just uses the one that appears later in the input file.)
